---
title: "Introducing {scheduler}"
subtitle: "Make recurring calendar events a little easier"
author: "James Laird-Smith"
date: "2019/09/12"
output:
  xaringan::moon_reader:
    css: ["default.css", "default-fonts.css", "jls.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
class: center, middle

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

# xaringan

### /ʃaː.'riŋ.ɡan/

---
class: large

- A schedule is a pattern of recurring calendar events.

- Schedules are hard.


---
# Comparison with `{ggplot2}`

.pull-left[
### `{ggplot2}`

- .red[**Data visualisations**] can occur in almost limitless variety.

- Implements a .red[**grammar of graphics**]
]

.pull-right[
### `{scheduler}`

- .red[**Schedules**] can occur in almost limitless variety.

- Implements a .red[**grammar of schedules**]
]
---

## Comparison with `{ggplot2}`
--

.pull-left[
### `{ggplot2}`
]
.pull-right[
### `{scheduler}`
]
--
.pull-left[
- .red[**Data visualisations**] can occur in almost limitless variety.
]
--
.pull-right[
- .red[**Schedules**] can occur in almost limitless variety.
]
--
.pull-left[
- Implements a .red[**grammar of graphics**]
]
--
.pull-right[
- Implements a .red[**grammar of schedules**]
]

---
# A boring regression

## A boring result:

```{r}
fit = lm(dist ~ 1 + speed, data = cars)
coef(summary(fit))
```

---
class: large
# Further work

- The {*vacationr*} package

- Wraps the most common country holidays.

---
class: large
# Practical applications

* Modelling with time series
 - Does the pattern change on holidays?
* Human resources
  - Calculating leave allowances
